Continuations via Negative Information Flow

### 2012-02-13 dual.tex
trace
_

@@

>>>>

Trace

\begin{center}
  \includegraphics{diagrams/trace.pdf}
\end{center}

@@

\item If we built an effect over {{langRevEE}}, say {{create}} and
  {{erase}}, are effects structured by an arrow or a monad now?

\item These functions aren't really values. There is no value one can
  produce that denotes a function. These functions are the ability to
  transform a value - the possibility of transforming a value.  In the
  product encoding of environments, there is no value one can assign
  to a variable such that it denotes a function.
